Notes on Validated Model Counting \\ Version of \today

### 2022-07-17 doc/mc-notes.tex
Fixed typo

The declaration of a $\pand$ operation has the form:
\begin{center}
\begin{tabular}{ccccccccc}
  \makebox[5mm]{$i$} & \makebox[5mm]{{\tt p}} & \makebox[5mm]{$v$} & \makebox[5mm]{$l_1$} & \makebox[5mm]{$l_2$} &
  \makebox[5mm]{$\cdots$} & \makebox[5mm]{$l_k$} & \makebox[5mm]{\tt 0} \\
\end{tabular}
\end{center}
where $i$ is a new clause ID, $v$ is a positive integer that does not
correspond to any previous variable, and $l_1, l_2, \ldots, l_k$ is a sequence of $k$  ($k \geq 2$)
integers representing literals of existing variables.  
This declaration implicitly causes $k+1$ clauses to be added to the proof:
\begin{center}
\begin{tabular}{cccccc}
\makebox[10mm]{ID} & \multicolumn{5}{c}{Clause} \\
  $i$ & $v$ & $-l_1$ & $-l_2$ & $\cdots$ & $-l_k$\\
  $i\!+\!1$ & $-v$ & $l_1$  \\
  $i\!+\!2$ & $-v$ & $l_2$  \\
  & $\ldots$ \\
  $i\!+\!k$ & $-v$ & $l_k$  \\
\end{tabular}
\end{center}
The dependency sets for the arguments represented each pair of literals $l_{j_1}$ and $l_{j_2}$, for $1 \leq j_1 < j_2 \leq k$, must be disjoint.

>>>>

The declaration of a $\pand$ operation has the form:
\begin{center}
\begin{tabular}{ccccccccc}
  \makebox[5mm]{$i$} & \makebox[5mm]{{\tt p}} & \makebox[5mm]{$v$} & \makebox[5mm]{$l_1$} & \makebox[5mm]{$l_2$} &
  \makebox[5mm]{$\cdots$} & \makebox[5mm]{$l_k$} & \makebox[5mm]{\tt 0} \\
\end{tabular}
\end{center}
where $i$ is a new clause ID, $v$ is a positive integer that does not
correspond to any previous variable, and $l_1, l_2, \ldots, l_k$ is a sequence of $k$  ($k \geq 2$)
integers representing literals of existing variables.  
This declaration implicitly causes $k+1$ clauses to be added to the proof:
\begin{center}
\begin{tabular}{cccccc}
\makebox[10mm]{ID} & \multicolumn{5}{c}{Clause} \\
  $i$ & $v$ & $-l_1$ & $-l_2$ & $\cdots$ & $-l_k$\\
  $i\!+\!1$ & $-v$ & $l_1$  \\
  $i\!+\!2$ & $-v$ & $l_2$  \\
  & $\ldots$ \\
  $i\!+\!k$ & $-v$ & $l_k$  \\
\end{tabular}
\end{center}
The dependency sets for the arguments represented by each pair of literals $l_{j_1}$ and $l_{j_2}$, for $1 \leq j_1 < j_2 \leq k$, must be disjoint.
